Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-02-27 eg6-letters/incoherent/incoherent_prl.tex
fix grammar

%conclusion
In summary, we have presented the first BSA measurement associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results are compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
result is a first step in using a novel experimental method of understanding 
the properties of bound nucleons directly from the basic degrees of freedom of 
QCD, quarks and gluons. Planned experiments at Jefferson Lab will continue 
and extend these studies of the bound nucleon structure using DVCS. We have 
an experimental program using the CLAS12 detector in the experimental Hall-B, 
called ALERT, to improve the DVCS measurements with the detection of nuclear
fragments to control better the final state interactions and the initial state
kinematic.

>>>>

%conclusion
In summary, we have presented the first BSA measurement associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results are compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
result is a first step in using a novel experimental method of understanding 
the properties of bound nucleons directly from the basic degrees of freedom of 
QCD, quarks and gluons. Planned experiments at Jefferson Lab will continue 
and extend these studies of the bound nucleon structure using DVCS. We have 
an experimental program using the CLAS12 detector in the experimental Hall-B, 
called ALERT, to improve the DVCS measurements with the detection of nuclear
fragments to better control the final state interactions and the initial state
kinematic.
